### 2025-01-31 Paper/CAGEO_LaTeXTemplate-main/main_document.tex
ff

In the study carried out by Song \citep{Song2006AFF} in this area in 2006, segmentation studies of rocks on Mars were carried out in order to plan the route and determine the landing areas. Texture-based image segmentation and edge-flow driven active contour has been developed. Wavelet based local transform, multi-resolution histograms, and inter-scale decision were combined and used for rock segmentation. As a result of the experiments, reliable rock segmentation results were obtained by Song.

@@

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV. An area was selected to create train images. Rock blocks within this area were labelled and mask images were created. Then segmentation process was completed by Python and necessary libraries, and the results were converted to the polygon as a vector file (Fig. \ref{fig:Figure3}). Moreover, the volumes of all the rocks were calculated.
This section includes an example of equation. 
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig3.jpg}
	\caption{ Workflow diagram}
	\label{fig:Figure3}
\end{figure}
\subsection{Data preparation}
In this study required data was collected by UAV. DJI phantom 3-Pro was used for image acquisition. First, the area to be flown is determined, then the necessary parameters for image acquisition are entered by the Pix4d Capture software. These parameters were chosen as follows.\\
– Flight altitude (altitude): 100 m.\\
– Flight speed (speed): Fast\\
– Camera angle (Angle): 70$^o$\\
– Overlap: 80\%\\

@@

An area was selected to create train and test images from large orthophoto image. This area was selected randomly. Then all rocks seen on the image were drawn on by GIS software. This file was saved as a vector file, and it will be used as mask data in segmentation processes. After this process, we have created the image and mask files. 
A deep learning model requires the same sizes of images. That's why a single image needs to be split into patches. The patch dimension was used as 256×256. Train-test splitting size was selected as 66\% for training data and 34\% for testing data. The large image was split into 9 part to avoid sampling from the same regions. Areas 1,5,9 were selected for creating test images. Train images were selected from the others (2,3,4,6,7,8) areas (Fig. \ref{fig:Figure4}). A total of 600 images (256×256) were selected, 369 images for training and 191 images for testing. The same processes were applied to extract the mask images.
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig4.jpg}
	\caption{ Train and test sampling areas. 1,5,9 test sampling area and 2,3,4,6,7,8 train sampling area}
	\label{fig:Figure4}
\end{figure}

@@

DenseNet121 transfer learning models were used for feature extraction and rock segmentation was performed with U-Net. Segmentation model was evaluated in terms of Intersection over Union (IoU) and f1-score metrics. For the calculate loss value dice loss was used. IoU, which is frequently preferred in segmentation problems, is also known as the Jaccard similarity coefficient \citep{jaccard1912distribution}. It is the ratio of correctly classified pixels to the sum of the number of pixels in that class and the predicted number of pixels. Mean IoU is the average IoU of all classes and presented in equation \ref{eqn:eq1}.

@@

U-Net segmentation model was used with DenseNet121. IOU and F1 score values were used as metrics. Model parameters were tested with different values. The parameters and values that provide the best results are given in the table\ref{tab:Table1} below.

@@

Hardware requirements:

>>>>

In the study carried out by Song \citep{Song2006AFF} in this field in 2006, segmentation studies of rocks on Mars were carried out in order to plan the route and determine the landing areas. Texture-based image segmentation and edge-flow driven active contour has been developed. Wavelet based local transform, multi-resolution histograms, and inter-scale decision were combined and used for rock segmentation. As a result of the experiments, reliable rock segmentation results were obtained by Song.

@@

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV. An area was selected to create train images. Rock blocks within this area were labelled and mask images were created. Then segmentation process was completed by Python and necessary libraries, and the results were converted to the polygon as a vector file (Fig. \ref{fig:Figure3}). Moreover, the volumes and 3D surfaces of all the rocks were calculated.
This section includes an example of equation. 
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig3.jpg}
	\caption{ Workflow diagram}
	\label{fig:Figure3}
\end{figure}
\subsection{Data preparation}
In this study required data was collected by UAV. DJI phantom 3-Pro was used for image acquisition. First, the area to be flown is determined, then the necessary parameters for image acquisition are entered by the Pix4d Capture software. These parameters were chosen as follows.\\
– Flight altitude (altitude): 100 m.\\
– Flight speed (speed): Fast\\
– Camera angle (Angle): 70$^o$\\
– Overlap: 80\%\\

@@

An area was selected to create train and test images from large orthophoto image. This area was selected randomly. Then all rocks seen on the image were drawn on by GIS software. This file was saved as a vector file and used as mask data in segmentation processes. After this process, we have created the image and mask files. 
A deep learning model requires the same sizes of images. That's why a single image needs to be split into patches. The patch dimension was used as 256×256. Train-test splitting size was selected as 66\% for training data and 34\% for testing data. The large image was split into 9 part to avoid sampling from the same regions. Areas 1,5,9 were selected for creating test images. Train images were selected from the others (2,3,4,6,7,8) areas (Fig. \ref{fig:Figure4}). A total of 600 images (256×256) were selected, 369 images for training and 191 images for testing. The same processes were applied to extract the mask images.
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig4.jpg}
	\caption{ Train and test sampling areas. 1,5,9 test sampling area and 2,3,4,6,7,8 train sampling area}
	\label{fig:Figure4}
\end{figure}

@@

DenseNet121 transfer learning models were used for feature extraction and rock segmentation was performed with U-Net. Segmentation model was evaluated in terms of Intersection over Union (IoU) and F1-score metrics. For the calculate loss value dice loss was used. IoU, which is frequently preferred in segmentation problems, is also known as the Jaccard similarity coefficient \citep{jaccard1912distribution}. It is the ratio of correctly classified pixels to the sum of the number of pixels in that class and the predicted number of pixels( Equation \ref{eqn:eq1}).

@@

U-Net segmentation model was used with DenseNet121. IOU and F1-score values were used as metrics. Model parameters were tested with different values. The parameters and values that provide the best results are given in the table\ref{tab:Table1} below.

@@
